### 2020-01-21 paper.tex
Quick notes on what to do

>>>>

\section{ToDos}

\begin{enumerate}
    \item Make sure that we loose nothing while preparing the short paper (backup: in branch, in directory(svn-style branch)?)
    \item Apply the ACM style and see how much space do we have
    \item Decide on the subset of results to publish (I would minimize those: if a figure on LB fits, it would be vital to include it)
    \item (and hence, draw a figure)
    \item Decide on the order of results
    \item Couple iterations on existing results (these are mostly fine already, though)
    \item Make an ACM account for the submission and sum up all the steps needed for the submission
\end{enumerate}
